Characteristic polynomial of p-adic matrices

### 2016-12-14 charpoly/charpoly.tex
A few words on the computation of the char poly by Hessenberg.

In this section, we combine the computation of an Hessenberg form
of a matrix and the computation of the inverse through the SNF
over a complete discrete valuation field
to compute $\com (X-A)$ and $d \chi.$

@@

@@

>>>>

In this section, we combine the computation of an Hessenberg form
of a matrix and the computation of the inverse through the SNF
over a complete discrete valuation field
to compute $\com (X-A)$ and $d \chi.$
%The computation of an Hessenberg form provides an $O(n^3)$
%algorithm to compute the characteristic polynomial.

@@

\begin{rem} \label{rem:char_pol_from_hessenberg}
From an Hessenberg form of $M,$ it is well known
that one can compute the characteristic polynomial of 
$M$ in $O(n^3)$ operations in $K.$ See \todo{cite Cohen} page
55 and 56.
However, this computation involves some divisions, and its
behaviour regarding to precision is not easy to
quantify.
\end{rem}

@@

\begin{rem}
As a consequence of the previous remark, once the optimal jagged
precision is known, it is possible to possible lift arbitrarily
the precision on $M$ and then to perform
a computation of the characteristic polynomial
from an Hessenberg form as in \ref{rem:char_pol_from_hessenberg},
in $O(n^3).$
By truncating afterward at the optimal jagged precision,
we can achieve by this way this optimal precision.
\end{rem}
